---
title: "Lower Cook Inlet Chinook marine sport harvest MSA"
author: "Andy Barclay"
date: "June 14, 2018"
output: html_document
---
##Set up workspace
###Get functions and load tidy packages
```{r workspace setup, echo=TRUE}

source("C:\\Users\\awbarclay\\Documents\\R\\GitHubCloneFunctions.R")#GCL functions
source("V:\\Analysis\\Staff\\Andy Barclay\\R\\New Functions\\WorkspaceFolders.GCL.R")#A function I wrote

library("tidyverse")

```

###Create output folders 
```{r create folders, echo=TRUE, message=FALSE}
#WorkspaceFolders.GCL(Folders=c("Output","objects","rubias"),Subfolders=list(rubias=c("baseline","mixture","output")),wd=getwd())

```

###Create locus control and get genotype data
```{r locus control, echo=TRUE}

#CreateLocusControl.GCL(markersuite = "LCI_Chinook_43SNPs", username ="awbarclay", password = password)#Locus control

sillyvec<-c("KCIMHO17","KCIMAP17","KCIMDC17")

#LOKI2R.GCL(sillyvec=sillyvec,username="awbarclay",password)#Pull Data from LOKI

#save.image("V:/Analysis/2_Central/Chinook/Lower Cook Inlet/LCI_2017/LCI_2017.Rdata")

load("V:/Analysis/2_Central/Chinook/Lower Cook Inlet/LCI_2017/LCI_2017.Rdata")
```
###Create initial locus object
The Cook Inlet genetic baseline was analyzed for a 96 SNP locus set.  To reduce analysis cost, the locus set was reduced to 24 loci with the highest FST values
```{r initial locus object}

loci <- LocusControl$locusnames
loci

```

##Data cleanup
###Check initial sample size
```{r initial sample size, echo=TRUE}

silly_N<-function(sillyvec){sapply(sillyvec,function(silly){get(paste0(silly,".gcl"))$n})}#Function for sample sizes

ColSize<-data.frame(row.names = sillyvec)
ColSize$Original_N <-silly_N(sillyvec)
ColSize

```
###Check genotypes by locus
This is the proportion of the samples with genotypes by locus
```{r sample size by locus}

SampSizeByLoc<-as.tibble(SampSizeByLocus.GCL(sillyvec,loci)/ColSize$Original_N) %>% 
  mutate(Collection=sillyvec) %>% 
  select(Collection,everything()) %>% 
  gather(key=Locus,value="Proportion",-Collection)

head(SampSizeByLoc)
```
#Heatmap to check for holes
```{r heatmap of genotype holes, fig.height=24, fig.width=20}

SampSizeByLoc %>% 
  ggplot(aes(Collection,Locus,fill=Proportion))+
  geom_tile()

```
###Removing individuals with <80% of loci with gentotypes
Fish that have gentoypes for less than 80% of loci are likely to have poor quality DNA and might introduce gentotyping errors into the mixture data and reduce the accruacy of the mixed stock analysis (MSA)
```{r missloci,echo=TRUE}

MissLOCI=RemoveIndMissLoci.GCL(sillyvec=sillyvec,proportion=0.8)
MissLOCI

ColSize$AfterMissLoci_N <- silly_N(sillyvec)
ColSize

```

###Check for duplicate individuals and remove them
Fish with 99% of scores that match
```{r dupckeck, echo=TRUE, message=FALSE}

dupcheck<-CheckDupWithinSilly.GCL(sillyvec=sillyvec,loci=loci,quantile=NULL,minproportion=0.99)

```
```{r remove duplicate fish,results="hide"}

DupsRemoved<-RemoveDups.GCL(dupcheck)#Remove one of the duplicates

```
```{r final sample size}
ColSize$Final_N <- silly_N(sillyvec)
ColSize

```
##Setup mixtures
###Create vector of mixture names
```{r mixvec, echo=FALSE}

mixvec<-c("LCI_Summer","LCI_Winter","UCI_Early","UCI_Late")  

```

###Get mixture IDs from attributes and create mixture .gcl objects
```{r attributes table}
attr<-bind_rows(set_names(lapply(sillyvec,function(silly){as.tibble(get(paste0(silly,".gcl"))$attributes)}),sillyvec))
attr
```
####LCI_winter
```{r LCI_winter}

LCI_Winter_IDs<-set_names(lapply(sillyvec,function(silly){
  
  attr %>% filter(CAPTURE_LOCATION=="LCI_Winter",SILLY_CODE==silly) %>% 
    select(FK_FISH_ID) %>% 
    as_vector() %>% 
    as.character()

}),sillyvec) %>% 
  purrr::compact()
  

PoolCollections.GCL(collections=names(LCI_Winter_IDs),loci = loci, IDs=LCI_Winter_IDs,newname = "LCI_Winter")
  
```
####LCI_Summer_IDs
```{r LCI_Summer_IDs}

LCI_Summer_IDs<-set_names(lapply(sillyvec,function(silly){
  
  attr %>% filter(CAPTURE_LOCATION=="LCI_Summer",SILLY_CODE==silly) %>% 
    select(FK_FISH_ID) %>% 
    as_vector() %>% 
    as.character()

}),sillyvec) %>% 
  purrr::compact()

PoolCollections.GCL(collections=names(LCI_Summer_IDs),loci = loci,IDs=LCI_Summer_IDs,newname = "LCI_Summer")

```
####UCI_Early_IDs
```{r UCI_Early_IDs}

UCI_Early_IDs<-set_names(lapply(sillyvec,function(silly){
  
  attr %>% filter(CAPTURE_LOCATION=="UCI_Early",SILLY_CODE==silly) %>% 
    select(FK_FISH_ID) %>% 
    as_vector() %>% 
    as.character()

}),sillyvec) %>% 
  purrr::compact()

PoolCollections.GCL(collections=names(UCI_Early_IDs),loci = loci,IDs=UCI_Early_IDs,newname = "UCI_Early")

```
####UCI_Late_IDs
```{r UCI_Late_IDs}

UCI_Late_IDs<-set_names(lapply(sillyvec,function(silly){
  
  attr %>% filter(CAPTURE_LOCATION=="UCI_Late",SILLY_CODE==silly) %>% 
    select(FK_FISH_ID) %>% 
    as_vector() %>% 
    as.character()

}),sillyvec) %>% 
  purrr::compact()

PoolCollections.GCL(collections=names(UCI_Late_IDs),loci = loci,IDs=UCI_Late_IDs,newname = "UCI_Late")

```
####Check mixture sample sizes
```{r sample size check}

silly_N(sillyvec=mixvec)

```

####Create rubias mixtures
```{r rubias mixtures}

rubias_mixtures <- lapply(mixvec,function(mix){
  
  create_rubias_mixture(sillyvec = mix,loci = loci, path = "rubias/mixture")
  
  }) %>% 
  
  set_names(mixvec)

```
##Set up baseline
###Get objects from baseline workspace
```{r baseline objects}

attach("V:/Analysis/2_Central/Chinook/Lower Cook Inlet/2015/Baseline/LowerCIChinook2015Baseline.RData")

PooledNames211<-PooledNames211

groupvec<-LCIgroupvec

#loci43<-loci43 this list of loci contains PSMB1 and not NRP, drop PSMB1 since it was not run on the mixture analysis project 
loci42<-loci43[29]

basefortran=CreateBaseline.GCL(sillyvec=PooledNames211,loci=loci42,dir="BAYES/Baseline",basename="LCI211pops42loci",type="BAYES",groupvec=NULL)

detach(pos=match(x="file:V:/Analysis/2_Central/Chinook/Lower Cook Inlet/2015/Baseline/LowerCIChinook2015Baseline.RData",table=search()))#Detach from baseline data.


```

